Common Concerns in BYOD Policies

### 2017-02-01 paper.tex
Tweaks based on reviewers

A more complex example can be taken from the NHS policy.
Employees are not allowed to call non-domestic, or premium rate numbers on company-owned phones, however an exception can be made if approved by the appropriate manager.
To implement this we have the default rule that international calls are banned, a second rule stating that it is allowed if an exemption is made, finally a third rule delegating the exemption making process to the employee's manager.
\begin{policyrule}{NHS}
  All mobile devices will be configured for national access only. Premium/international calls will be barred. 
  International call barring and roaming arrangements can be lifted for specific periods, to be stipulated on request, on approval of the relevant manager/budget holder.
  \begin{lstlisting}
'nhs-trust' says Device canCall(TelephoneNumber:X) 
  if Device isOwnedBy('nhs-trust'),
     X isNationalNumber, X isStandardRateNumber.

@@

Comparing the policies we found a diverse range of concerns.
Some of these concerns (the use of acknowledgements in particular) are not addressed by current BYOD tools. 
The tools focus on device configuration, which are only part of the concerns of the BYOD policies.
We also found the policies were presented in a variety of styles.
Some, like SANS, are prescriptive and describe a company telling employees what to do.
Others, like HiMSS, take the form of a user contract, where employees state that they acknowledge the companies rules and agree to follow them.
The lack of commonality suggest there may be no perfect solution for implementing BYOD policies.
Future tools must be flexible enough to express a range of policies, and model the trust relationships these policies contain.

>>>>

A more complex example can be taken from the NHS policy.
Employees are not allowed to call non-domestic, or premium rate numbers on
company-owned phones~\footnote{The NHS policy frequently doesn't distinguish between
  company and privately owned phones and applies to both.}, however an exception can be made if approved by the appropriate manager.
To implement this we have the default rule that international calls are banned, a second rule stating that it is allowed if an exemption is made, finally a third rule delegating the exemption making process to the employee's manager.
\begin{policyrule}{NHS}
  All mobile devices will be configured for national access only. Premium/international calls will be barred.
  International call barring and roaming arrangements can be lifted for specific periods, to be stipulated on request, on approval of the relevant manager/budget holder.
  \begin{lstlisting}
'nhs-trust' says Device canCall(TelephoneNumber:X)
  if Device isOwnedBy('nhs-trust'),
     X isNationalNumber, X isStandardRateNumber.

@@

Comparing the policies we found a diverse range of concerns.
Some of these concerns (the use of acknowledgements in particular) are not addressed by current MDM tools.
The tools focus on device configuration, which are only part of the concerns of the BYOD policies.
We also found the policies were presented in a variety of styles.
Some, like SANS, are prescriptive and describe a company telling employees what to do.
Others, like HiMSS, take the form of a user contract, where employees state that they acknowledge the companies rules and agree to follow them.
The lack of commonality suggest there may be no perfect solution for implementing BYOD policies.
Future tools must be flexible enough to express a range of policies, and model the trust relationships these policies contain.
